---
title: "International COVID-19 risk areas"
subtitle: "as designated by the German government"
permalink: /en
header_type: hero
excerpt: |
  The interactive map allows you to explore
  Germany's current risk designation worldwide.
  Click in a specific country to read more details
  about that country and its regions
  regarding traveling to Germany.
always_allow_html: yes
output: 
  md_document:
    preserve_yaml: true
    variant: gfm
---


<!-- Modify _R/index_es.Rmd file instead -->

```{r, child='snippets/setup.Rmd'}
```

```{r load_table, echo=FALSE}
db_table <- readr::read_csv("../assets/dist/db_countries_risk_en.csv")
```

<p class="text-right font-weight-bold">Updated on `r format(date, format="%d %B %Y")`</p>

## Risk map

The interactive map allows you to explore
Germany's current risk designation worldwide.
Click in a specific country to read more details
about that country and its regions
regarding traveling to Germany.

<div id="leaflet" style="width:100%;height:75vh;" class="leaflet html-widget"></div>
<script src="https://corona-atlas.de/assets/data/locale_en.js"></script> 
<script src="https://corona-atlas.de/assets/js/map.js"></script>

All information is directly fetched from the Robert Koch Institut and supplied without guarantee.
For a complete up-to-date overview on all international risk areas
visit [rki.de/risikogebiete](https://rki.de/risikogebiete).

The current travel restrictions for risk areas
are published on
[the website of the German Federal Ministry of Health](https://www.bundesgesundheitsministerium.de/en/coronavirus/current-information-for-travellers).

## Database

You can also browse the countries directly on the database.

```{r, child='snippets/table.Rmd'}
```

<p class="text-center my-5">
  <a href="assets/dist/db_countries_risk_en.csv" class="btn btn-primary">Download database (CSV)</a>
</p>
