---
title: "International COVID-19 risk areas"
subtitle: "as designated by the German government"
permalink: /en
always_allow_html: yes
output: 
  md_document:
    preserve_yaml: true
---


<!-- Modify _R/index_en.Rmd file instead -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```



```{r data_cleansing, echo=FALSE}

library(giscoR)
library(sf)
library(readr)
library(dplyr)
library(countrycode)
library(leaflet)
library(reactable)
library(rmarkdown)
library(leaflet.providers)

data <- readr::read_csv("../assets/data/db_countries.csv")
rl <- readr::read_csv("../assets/data/risk_level_code.csv")



date <- data %>% filter(ISO3_CODE == "Field date") %>%
  select(risk_level_code) %>% as.character() %>% as.Date()


cntries_shape <-
  gisco_get_countries(
    year = 2020,
    epsg = 4326,
    cache_dir = "./geojson",
    resolution = 20
  )

# Get NUTS units
data_units <- data %>% filter(region == TRUE & !is.na(NUTS_CODE))

if (nrow(data_units > 0)) {
  nuts_shape <- gisco_get_nuts(
    year = 2021,
    epsg = 4326,
    cache_dir = "./geojson",
    resolution = 20,
    nuts_id = c(data_units$NUTS_CODE, "ES") # Hack
  )
  
  nuts_shape_end <- nuts_shape %>%
    mutate(NUTS_CODE = NUTS_ID,
           name.en = NAME_LATN,
           name.de = NAME_LATN) %>%
    select(NUTS_CODE, name.en, name.de) %>% inner_join(data_units) %>%
    select(ISO3_CODE, name.en, name.de, risk_level_code)
  
  # Get LAU
  data_lau <-
    data_units %>% filter(!NUTS_CODE %in% nuts_shape$NUTS_ID)
  if (nrow(data_lau) > 0) {
    lau_shape <- gisco_get_lau(
      year = 2019,
      epsg = 4326,
      cache_dir = "./geojson",
      gisco_id = c(data_lau$NUTS_CODE, "AL_AL111") # Hack
    )
    
    lau_shape_end <- lau_shape %>%
      mutate(NUTS_CODE = GISCO_ID,
             name.en = LAU_NAME,
             name.de = LAU_NAME) %>%
      inner_join(data_units) %>%
      select(ISO3_CODE, name.en, name.de, risk_level_code)
    
  } else {
    lau_shape_end <- NULL
  }
  
  
  regions_end <-
    bind_rows(nuts_shape_end, lau_shape_end) %>% mutate(region = TRUE)
  
  
  # Substract regions from countries
  
  cntries_shape_reg <-
    st_difference(cntries_shape, st_union(regions_end))
  
} else {
  cntries_shape_reg <- cntries_shape
  regions_end <- NULL
}

# Add Kosovo
K <- st_read("./geojson/kosovo.geojson", quiet = TRUE) %>% select(ISO3_CODE)

cntries_shape_reg <-
    st_difference(cntries_shape_reg, st_union(K))

cntries_shape_reg <- bind_rows(cntries_shape_reg, K)

data_cntries <- data %>% filter(is.na(region)) %>%
  mutate(name.en = NAME_ENGL,
         name.de = countrycode(ISO3_CODE, "iso3c", "cldr.name.de")) %>%
  select(ISO3_CODE, name.en, name.de, risk_level_code) %>% distinct() %>%
  mutate(name.de = ifelse(is.na(name.de),
                          name.en,
                          name.de))



cntries_shape_reg2 <- cntries_shape_reg %>%
  select(ISO3_CODE) %>%
  inner_join(data_cntries)

all_shapes <- bind_rows(cntries_shape_reg2, regions_end)
all_shapes <- st_make_valid(all_shapes)

df_labels <- data_cntries %>% mutate(cntry.en = name.en,
                                     cntry.de = name.de) %>%
  select(ISO3_CODE, cntry.en, cntry.de)

# Labels
all_shapes <- all_shapes %>% left_join(df_labels)

all_shapes$label_en <- ifelse(
  !is.na(all_shapes$region),
  paste0(all_shapes$cntry.en, " | ", all_shapes$name.en),
  all_shapes$name.en
)
all_shapes$label_de <- ifelse(
  !is.na(all_shapes$region),
  paste0(all_shapes$cntry.de, " | ", all_shapes$name.de),
  all_shapes$name.de
)

all_shapes <-
  all_shapes %>% select(ISO3_CODE, label_en, label_de, risk_level_code) %>% mutate(risk_level_code = as.integer(risk_level_code)) %>% left_join(rl)

DEU <- all_shapes %>% filter(ISO3_CODE == "DEU")
level0 <- all_shapes %>% filter(risk_level_code == "0",
                                ISO3_CODE != "DEU")
level1 <- all_shapes %>% filter(risk_level_code == "1")
level2 <- all_shapes %>% filter(risk_level_code == "2")
level3 <- all_shapes %>% filter(risk_level_code == "3")
level4 <- all_shapes %>% filter(risk_level_code == "4")
```

<p class="text-right font-weight-bold">Updated on `r format(date, format="%d %B %Y")`</p>

## Risk map

The interactive map allows you to explore
Germany's current risk designation worldwide.
Click in a specific country to read more details
about that country and its regions
regarding traveling to Germany.

```{r map, echo=FALSE, out.width = "100%", out.height="75vh"}

labs <- rl$risk_level_en
labs <- labs[c(2:5, 1)]


labelsDEU <- sprintf("<strong>%s</strong><br/>%s",
                     DEU$label_en,
                     DEU$risk_level_en) %>% lapply(htmltools::HTML)

label0 <- sprintf("<strong>%s</strong><br/>%s",
                  level0$label_en,
                  level0$risk_level_en) %>% lapply(htmltools::HTML)

label1 <- sprintf("<strong>%s</strong><br/>%s",
                  level1$label_en,
                  level1$risk_level_en) %>% lapply(htmltools::HTML)


label2 <- sprintf("<strong>%s</strong><br/>%s",
                  level2$label_en,
                  level2$risk_level_en) %>% lapply(htmltools::HTML)

label3 <- sprintf("<strong>%s</strong><br/>%s",
                  level3$label_en,
                  level3$risk_level_en) %>% lapply(htmltools::HTML)

label4 <- sprintf("<strong>%s</strong><br/>%s",
                  level4$label_en,
                  level4$risk_level_en) %>% lapply(htmltools::HTML)

map <- leaflet(options = leafletOptions(minZoom = 0.5)) %>%
  setMaxBounds(-180,-90, 180, 90) %>%
  addProviderTiles("CartoDB.Voyager", group = "Carto Voyager") %>%
  addProviderTiles("CartoDB.DarkMatter", group = "Carto Dark Matter") %>%
  addProviderTiles("Esri.WorldImagery", group = "Esri World Imagery") %>%
  addTiles(urlTemplate = "", attribution = "© EuroGeographics for the administrative boundaries") %>%
  setView(lat = 51.705533, lng = 11.8124408, zoom = 4) %>%
  addPolygons(
    data = DEU,
    color = "#44444",
    weight = 0.5,
    smoothFactor = .1,
    opacity = 1,
    fillColor = "blue",
    fillOpacity = 0.5,
    highlightOptions = highlightOptions(
      color = "white",
      weight = 1,
      bringToFront = TRUE
    ),
    popup = labelsDEU
  ) %>%
  addPolygons(
    data = level0,
    color = "#44444",
    weight = 0.5,
    smoothFactor = .1,
    opacity = 1,
    fillColor = "green",
    fillOpacity = 0.5,
    group = labs[5],
    highlightOptions = highlightOptions(
      color = "white",
      weight = 1,
      bringToFront = TRUE
    ),
    popup = label0
  ) %>%
  addPolygons(
    data = level1,
    color = "#44444",
    weight = 0.5,
    smoothFactor = .1,
    opacity = 1,
    fillColor = "red",
    fillOpacity = 0.5,
    group = labs[1],
    highlightOptions = highlightOptions(
      color = "white",
      weight = 1,
      bringToFront = TRUE
    ),
    popup = label1
  ) %>%
  addPolygons(
    data = level2,
    color = "#44444",
    weight = 0.5,
    smoothFactor = .1,
    opacity = 1,
    fillColor = "orange",
    fillOpacity = 0.5,
    group = labs[2],
    highlightOptions = highlightOptions(
      color = "white",
      weight = 1,
      bringToFront = TRUE
    ),
    popup = label2
  ) %>%
  addPolygons(
    data = level3,
    color = "#44444",
    weight = 0.5,
    smoothFactor = .1,
    opacity = 1,
    fillColor = "yellow",
    fillOpacity = 0.5,
    group = labs[3],
    highlightOptions = highlightOptions(
      color = "white",
      weight = 1,
      bringToFront = TRUE
    ),
    popup = label3
  ) %>%
  addPolygons(
    data = level4,
    color = "#44444",
    weight = 0.5,
    smoothFactor = .1,
    opacity = 1,
    fillColor = "#00FF00",
    fillOpacity = 0.5,
    group = labs[4],
    highlightOptions = highlightOptions(
      color = "white",
      weight = 1,
      bringToFront = TRUE
    ),
    popup = label4
  ) %>%
  addEasyButton(easyButton(
    icon = "fa-globe",
    title = "",
    onClick = JS(
      "function(btn, map){ map.setView([ 51.705533,11.8124408],4); }"
    )
  )) %>%
  addLayersControl(
    baseGroups = c("Carto Voyager", "Carto Dark Matter", "Esri World Imagery"),
    overlayGroups = labs,
    options = layersControlOptions(collapsed = TRUE)
  ) %>%
  addLegend(
    colors = c("red", "orange", "yellow", "#00FF00", "green"),
    labels = labs,
    position = "bottomleft"
  ) %>% #RHH
  htmlwidgets::onRender(
    "
        function() {
            $('.leaflet-control-layers-overlays').prepend('<strong>Risk level</strong>');
        }
    "
  )
map
```

All information is directly fetched from the Robert Koch Institut and supplied without guarantee.
For a complete up-to-date overview on all international risk areas and the travel restrictions that apply to them
based on their risk designation,
visit the [website of the RKI](https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Risikogebiete_neu.html).

## Database

You can also browse the countries directly on the database.

<script src="https://cdn.jsdelivr.net/gh/dieghernan/RKI-Corona-Atlas/_R/plugins/reactable-binding-0.2.3/reactable.min.js"></script>
```{r table , echo=FALSE}


df <- st_drop_geometry(all_shapes) %>%
  select(label_en, risk_level_en)

names(df) <- c("Country/Region", "Risk Level") #RHH

df <- df[order(df[, 1]), ]

reactable(
  df,
  filterable = TRUE,
  searchable = TRUE,
  showPageSizeOptions = TRUE,
  striped = TRUE,
  paginationType = "jump"
)

```

<!-- DHH - Maybe style as button -->
[Download database (CSV)](assets/data/db_countries.csv)
